On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate

### 2016-07-26 Main.Rmd
明日には0稿完成。3347 words.

---
title: "On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
csl: ECB.csl
output:
    html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: F
    fig_caption: true
    pandoc_args: [
      "--latexmathml"
    ]
# word_document:
#   toc: true
#   fig_caption: true
#   pandoc_args: [
#   "--latexmathml"
#   ]
---

@@

opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5, out.width = '500pixel', out.heit = '500pixel', dpi = 200, fig.align = "center", message = FALSE, warning = FALSE, cache = F, eval = T)
```

@@

InteractionDat <-
  data_frame(X = rep(X_range, times = 2),
           ETR = c(sqrt(dbeta(X_range, 4.5, 3)) * 1.1, sqrt(dbeta(X_range, 3, 4.5))),
           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))

@@

InteractionView <-
  InteractionDat %>%
  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
  theme_bw2() +
  theme(axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major = element_blank()) +
  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
  geom_line() +
  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
  geom_text(data = InteractionText, aes(label = labels), vjust = 1) +
  scale_fill_manual(values = c("white", "black")) +
  scale_linetype_manual(values = c(2, 1)) +
  scale_x_continuous(breaks = c(0.1, 0.9), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
  xlab("PSII-biased level of measuring light") +
  ylab("Relative electron transport rate") +
  gg_y(c(0, 2))
```

@@

  The photosynthetic rate is one of the most important and fundamental phenotype in the plant sciences.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
  The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
  The effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters in agricultural and horticultural studies.
  Therefore, the accurate measurements of the photosynthetic rate must be essential.
  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a single-level SPD of measuring light irrespective of the leaf growth conditions in these fields.
  The most widely-used measuring light might be mixture of blue + red LED light (BR-light) provided by light sources installed in commercial photosynthesis analyzing systems.
  The use of the artificial light sources might enable precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf thereby ensure the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that the measurements with a SPD of light different from growth light do not necessarily reflect the functioning of the photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and a sunlight-like SPD of light.
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable *P*~n~ under the sunlight.
  **In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~**.
  If the plants were evaluated without considering the interactions, the selection and decision might be distorted.

  In this short article, we introduce several articles reporting the interaction and the likely causes---the distribution of the excitation energy between the photosystems.
  Subsequently we suggest the situations where the interaction should be cared.
  We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited review articles on these topics are available.

@@

  The knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the electron transport, and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  **The excitation energy  the photosystems and their anntena complexes is transferred to the reaction centers, and then consumed photochemical reactions in the unit of mol**
  **Note that the term "energy" is used in **
  **The two photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).**
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1A).
  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1D).
  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
  An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

@@

  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
  On contrary, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the EED is a determinant of the distribution under a given SPD of light.
  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
  A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

@@

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
  A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Walters_Horton1995aPlanta showed the interaction in the O~2~ evolution yield using halogen lamp and color-conversion filter.
  @Hogewoning_et_al2012PC found the interaction in the *P*~n~ using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
  They demonstrated that the interaction can occur 違う組合せでも**.
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.

  <!-- A similar trends were observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP] (Table. 1). -->

  The distribution properties of a leaf seems to be tuned to the SPD of growth light, and thereby is expected to perform a higher photosynthetic quantum yield under **light the same PSII-biased level to growth light** (Fig. 2).
  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased by the interaction.

@@

  This interaction may have considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ saturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
  In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
  <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
  <!-- In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified. -->
  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction. -->

  The mechanisms of the SPD acclimation of the EED property are not yet fully elucidated [see @Murakami_et_al2016PP].
  <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
  <!--' They also found no difference in the stoichiometry between the leaves grown with and without supplemental FR [@Walters_Horton1995bPlanta]. -->
  <!--' Chow and coworkers also reported  -->
  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to represent different EED properties.

  For this decade, a number of studies have investigated the effects of the SPD of growth light on the plant growth and photosynthesis [e.g. @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
  Assimilation light provided by most of artificial light sources contain little FR.
  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs emit typical PSII-light (Supplemental Information S1).
  This is because FR is not "photosynthetically active" and FR-rich light promotes excessive stem elongation.
  <!-- It should be kept in the mind that the *P*~n~ of leaves grown under these light sources can be overestimated if measured with BR-light, and the measured *P*~n~ might be different from those under the PSI-light such as sunlight (Fig. 3XXX). -->
  <!-- When the response under sunlight is the interest of the experiment, we should carry out measurements under sunlight. -->
  On the other hand, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
  Since FR overexcites PSI, leaves grown under PSII-light supplemented with FR LED can become relatively PSI-leaves like EED property compared to those grown without supplemental FR.
  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR using BR-light might result in typical biased evaluation caused by the interaction, as is demonstrated in the previous report [@Murakami_et_al2016PP].

@@

  Further investigation is required to elucidate the extent of the interaction in the *P*~n~ under the above mentioned conditions.
  Note that such an interaction should be taken into account in the evaluations of the other photosynthesis-related characteristic, such as chl fluorescence parameters.
  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. Hogewoning_et_al2012PC].
  Imbalance in the excitation balance between the photosystems is supposed to acceralate the photoinhibition [@].
  Chl fluorescence parameters such as *F*~q~′/*F*~m~′ (PSII operating efficiency, also known as Φ~PSII~ and *Y*~II~) and photoinhibition indicator such as **Fv/Fm** should be measured with particular care.

# How the photosynthetic responses should be measured

  Ideally, the photosynthetic rates should be measured under the *in situ* conditions.
  In the prospective study focusing on the plant growth after the *P*~n~ measurements, the rates should be measured under the SPD of light the plant will subject to.
  For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g. @Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
  <!-- For instance, commercial transplants are sometimes raised in a closed system with artificial lighting [e.g. @Kozai2007POP], and subsequently transferred to a greenhouse and cultivated under sunlight. -->
  <!-- Therefore, in comparisons of light sources with different SPDs for the transplant production, *P*~n~ measurements should be made under sunlight. -->
  Note that the effect of the interaction seems to be less prominent than those of the other factors, such as the incident PPFD.
  The *P*~n~ measurements under sunlight, which usually generates fluctuations in the incident PFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
  The use of artificial light sources will lower the uncertainty caused by the fluctuations in the incident PPFD at the expense of the biases possibly caused by the interaction.
  This is because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.
  To solve this dilenma between the *in situ* evaluation and the PPFD stability, the SPD-controllable light source might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].

  In the retrospective study elucidating the causes of the differences in the experimental groups, the rates should be measured under the SPDs of light the plants recieved during the treatments.
  <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved. -->
  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using white LED for the plants grown under white LEDs light and using fluorescent lamps for those grown under fluorescent lamps.

  In both the prospective and retrospective studies, these simple solutions will eliminate the problems caused by the interaction.
  On the other hand, if the SPD of light the leaves will receive is not predetermined, then *P*~n~ should be measured under both PSII- and PSI-light.
  Researchers had better describe the "general" photosynthetic characteristics of the leaves in these kind of studies.
  Therefore, the interaction should be tested so as not to make biased evaluation.
  If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.
  If any the interaction, the results should not be generalized.
  The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.
  When the measuments were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
  <!-- The effect of the incteraction should be amplified in the comparison be the leaves with different EED properties. -->
  <!-- The interaction should be taken special care when the cases described in the **former section**. -->

@@

```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd", fig.width = 7.5, fig.height = 7.5, out.width = '500pixel', out.heit = '500pixel', dpi = 200}

>>>>

---
title: "On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
csl: ECB.csl
output:
    html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: T
    fig_caption: true
    pandoc_args: [
      "--latexmathml"
    ]
# word_document:
#   toc: true
#   fig_caption: true
#   pandoc_args: [
#   "--latexmathml"
#   ]
---

@@

opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5,
               out.width = '500pixel', out.heit = '500pixel', dpi = 200,
               message = FALSE, warning = FALSE, cache = F, eval = T)
```

@@

InteractionDat <-
  data_frame(X = rep(X_range, times = 2),
           ETR = c(sqrt(dbeta(X_range, 4.5, 3.5)) * 1.1, sqrt(dbeta(X_range, 3, 5))),
           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))

@@

InteractionView <-
  InteractionDat %>%
  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
  theme_bw2() +
  theme(axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major = element_blank()) +
  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
  geom_line() +
  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
  geom_text(data = InteractionText, aes(label = labels), vjust = 1) +
  scale_fill_manual(values = c("white", "black")) +
  scale_linetype_manual(values = c(2, 1)) +
  scale_x_continuous(breaks = c(0.07, 0.92), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
  xlab("PSII/PSI-biased level of measuring light") +
  ylab("Relative electron transport rate") +
  gg_y(c(0, 2))
```

@@

  The photosynthetic rate is one of the most important and fundamental trait of the plant.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
  The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
  The effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters in agricultural and horticultural studies.
  Therefore, the accurate measurements of the photosynthetic rate must be essential.
  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a single-level SPD of measuring light irrespective of the leaf growth conditions in these fields.
  The most widely-used measuring light might be mixture of blue + red LED light (BR-light) provided by light sources installed in commercial photosynthesis analyzing systems.
  The use of the artificial light sources might enable precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf thereby ensure the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that the measurements with a SPD of light different from growth light do not necessarily reflect the functioning of the photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and a sunlight-like SPD of light.
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable under artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable rates under the sunlight.
  **In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~**.
  If the plants were evaluated without considering the interactions, the selection and decision might be distorted.

  In this short article, we introduce a likely cause of the interaction and several articles reporting the interaction.
  We then suggest the situations where the interaction should be cared.
  We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], the photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited review articles on these topics are available.

@@

  Fundamental knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the electron transport and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  The excitation energy transferred to the reaction centers of the photosystems is consumed by the photochemical reactions in units of moles.
  The serial photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1C).
  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1B).
  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed photons---becomes smaller.
  An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

@@

  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an imbalanced excitation was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the EED is a determinant of the EED under a given SPD of light.
  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI based on the relative scale, not on the absolute scale.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-light-grown leaves (Fig. 1A), can overexcite PSII in PSI-light-grown leaves (Fig. 1C).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

@@

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light (Fig. 2).
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under light provided by cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light), and subsequently measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under the PSII- and PSI-light.
  When measured under the PSII-light, the yield was higher in the PSII-light-grown leaves; when measured under the PSI-light, the yield was higher in the PSI-light-grown leaves.
  A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Hogewoning_et_al2012PC observed the interaction in the photosynthetic quantum yield of CO~2~ uptake using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
  They demonstrated that the interaction cannot occur only in the case growth light was used as measuring light but also in the case the other SPDs of light was used.
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.

  These reports might suggest that the EED propertiy of a leaf is tuned to the **PSII/PSI-biased level of** growth light.
  It is expected that a leaf performs a higher ETR per absorbed photons by the photosystems under **measuring light with the same PSII/PSI-biased level to that of growth light** (Fig. 2).
  When leaves grown under different SPDs of light are compared and evaluated under a single-level SPD of light, the results should be inevitably biased depending on the SPD of measuring light.

@@

  This interaction may have considerable impact on the *P*~n~ especially in the measurements under the low PPFD and/or high CO~2~ concentration, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
  In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attention on the interaction.
  <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
  <!-- In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified. -->
  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction. -->

  The mechanisms of the SPD acclimation of the EED property have not yet been fully elucidated [see @Murakami_et_al2016PP].
  <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
  <!--' They also found no difference in the stoichiometry between the leaves grown with and without supplemental FR [@Walters_Horton1995bPlanta]. -->
  <!--' Chow and coworkers also reported  -->
  Considering the sensitively adjusted the photosystem stoichiometry in response to the SPD of growth light reported in  @Walters_Horton1995aPlanta, the interaction should be always taken into account whenever the *P*~n~ and related parameters are evaluated.
  The impacts of the interaction on the *P*~n~ should be paid particular attention, at least when the measured leaves are expected to represent different EED properties.

  For this decade, a number of studies have investigated the effects of the SPD of growth light on the plant growth and photosynthesis [e.g. @Matsuda_et_al2004PCP; @Matsuda_et_al2007SSPN; @Matsuda_et_al2008PCP; @Hogewoning_et_al2010aJXB; @Hogewoning_et_al2010bJXB; @Shibuya_et_al2015BP; @Trouwborst_et_al2016EEB].
  Assimilation light provided by most of artificial light sources contain little FR.
  In general, fluorescent lamps, metal halide lamps, high-pressure sodium lamps, and blue, red, and white LEDs emit typical PSII-light (Supplemental Information S1).
  This is because FR is not "photosynthetically active" and FR-rich light promotes excessive stem elongation.
  <!-- It should be kept in the mind that the *P*~n~ of leaves grown under these light sources can be overestimated if measured with BR-light, and the measured *P*~n~ might be different from those under the PSI-light such as sunlight (Fig. 3XXX). -->
  <!-- When the response under sunlight is the interest of the experiment, we should carry out measurements under sunlight. -->
  On the other hand, several recent papers suggest the significance of supplemental FR on the plant growth and development [for a review, see @Demote-Mainard_et_al2016EEB].
  Since FR overexcites PSI, leaves grown under PSII-light supplemented with FR LED can represent relatively PSI-leaves like EED property compared to those grown without supplemental FR.
  Therefore, comparing the *P*~n~ of leaves grown with and without supplemental FR using BR-light might result in typical biased evaluation caused by the interaction, as demonstrated in the previous report [@Murakami_et_al2016PP].

@@

  Note that such an interaction might have impacts on the other characteristics related to the photosynthetic electron transport, such as chl fluorescence parameters and the photoinhibition indicators.
  The overexicitation of PSII (or PSI) results in the lowered photochemical yield at PSII (or PSI) [e.g. @Hogewoning_et_al2012PC; @Laisk_et_al2014BBA], and the imbalance in the excitation should hastes the photoinhibition caused by the reactive oxygen species.
  Evaluation of these characteristics should also be measured with particular care on the interaction.

# How the photosynthesis should be measured

  Ideally, the photosynthetic rates and related parameters should be measured under the *in situ* conditions.
  In the prospective study focusing on the plant growth after the measurements, the measurements should be made under the SPD of light the plant will subject to.
  For instance, evaluation of the photosynthesis of the transplants grown under artificial lighting [e.g. @Kozai2007POP] should be made under sunlight because they are subsequently transferred to a greenhouse and cultivated under sunlight.
  Note that the effect of the interaction seems to be less prominent than those of the other factors, such as the incident PPFD.
  The measurements under sunlight, which usually causes fluctuations in the incident PPFD, should be avoided and thus the measurements should be made under the artificial light sources to ensure the reproducibility and reliability of the research.
  The use of artificial light sources will mitigate the uncertainty caused by the fluctuations in the incident PPFD at the expense of the biases possibly caused by the interaction.
  This is because the SPD of light from an artificial light source is generally by far different from that of *in situ* light.
  To solve this dilenma between the *in situ* evaluation and the PPFD stability, the SPD-controllable light source might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc].

  In the retrospective study aiming to elucidate the causes of the differences between the experimental groups, the measurements should be made under the SPDs of light the plants recieved during the treatments.
  <!-- When the aim of the research is to analyze the origins of the differences in the growth of the plants subject to several light treatments, the rates should be measured under the SPDs of light the plants recieved. -->
  For instance, when the difference in the resultant dry weight between the plants grown under white LEDs and fluorescent lamps are analyzed and the *P*~n~ is used for the explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs light and using the fluorescent lamps for those grown under fluorescent lamps.
  In both the prospective and retrospective studies, these simple solutions will eliminate the problems caused by the interaction.

  If the SPD of light the leaves will receive is not predetermined, then the measurements should be made under several levels of SPDs of light including PSII- and PSI-light.
  Researchers had better describe the "general" characteristics of the leaves in these kind of studies.
  **Therefore, the interaction should be tested so as not to make biased evaluation.**
  **If the significant interaction is not detected in two-way ANOVA, the main effect of the treatment can be assessed.**
  **If any the interaction, the results should not be generalized.**
  **The responses of the rates to both PSII- and PSI-light should be measured, compared, and reported in the paper.**
  When the measuments were made only under a single-level of SPD of measuring light because of unavoidable circumstances, the light source must be declared in the materials and methods section so that readers can follow the SPD.
  <!-- The effect of the incteraction should be amplified in the comparison be the leaves with different EED properties. -->
  <!-- The interaction should be taken special care when the cases described in the **former section**. -->

@@

```{r child = "~/Dropbox/Publish/ECB2016Review/Sup1.Rmd"}
